Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Fix typo

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to reqire more details and drive the
implementation closer to the desired goal.  Rinse and repeat.

@@

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and extended
    Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

\begin{quote}
    sol: @kazu: Can you add the documentation of \verb|test-shouldbe|
    to the bib, and cite it here?
\end{quote}

\noindent All combinators introduced in \ref{} have been
implemented~\cite{todo}; and they will be incorporated into a future
release of Hspec.
The implementation is trivial, so we will not further discuss it.

@@

\noindent Note that the {\tt placeholders} library provide better keyword such as {\tt notImplemented} and {\tt todo}.
Next we write user documentation in Haddock markup:

@@

\begin{itemize}
\item We use a preprocessor (the {\tt hspec-discover} package) to automatically generate this boilerplate.
\end{itemize}

@@

We do not get source locations for failing tests. Doctest solves this.
For Hspec/QuickCheck/HUnit something like JHC's
\verb|SRCLOC_ANNOTATE|
pragma~\cite{todo}
could help.

>>>>

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to require more details and drive the
implementation closer to the desired goal.  Rinse and repeat.

@@

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest\footnote{%
    http://hackage.haskell.org/package/doctest}, and extended
    Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

\noindent All combinators introduced in \ref{sec:code-doc} have been
implemented in the {\tt hspec-shouldbe} package\footnote{%
http://hackage.haskell.org/package/hspec-shouldbe};
and they will be incorporated into a future
release of Hspec.
The implementation is trivial, so we will not further discuss it.

@@

\noindent Note that the {\tt placeholders} library provides better keywords such as {\tt notImplemented} and {\tt todo} and they tells source locations when executed.
Next we write user documentation in Haddock markup:

@@

\begin{itemize}
\item We use a preprocessor (the {\tt hspec-discover} package\footnote{%
http://hackage.haskell.org/package/hspec-discover}) to automatically generate this boilerplate.
\end{itemize}

@@

We do not get source locations for failing tests. Doctest solves this.
For Hspec/QuickCheck/HUnit something like JHC's
\verb|SRCLOC_ANNOTATE|
pragma\footnote{%
http://repetae.net/computer/jhc/jhc.shtml} could help.
